---
title: "Untitled"
author: "Nima Ramezani Taghiabadi"
date: "20/02/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)



library(dplyr)
library(networkD3)
library(tidyr)
datapath = "~/Documents/data/miscellaneous/" 
# read in EU referendum results dataset
refresults <- read.csv(datapath %>% paste0("EU-referendum-result-data.csv"))
# aggregate by region
results <- refresults %>% 
  dplyr::group_by(Region) %>% 
  dplyr::summarise(Remain = sum(Remain), Leave = sum(Leave))

# format in prep for sankey diagram
results <- tidyr::gather(results, result, vote, -Region)
# create nodes dataframe
regions <- unique(as.character(results$Region))
nodes <- data.frame(node = c(0:13), 
                    name = c(regions, "Leave", "Remain"))
#create links dataframe
results <- merge(results, nodes, by.x = "Region", by.y = "name")
results <- merge(results, nodes, by.x = "result", by.y = "name")
links <- results[ , c("node.x", "node.y", "vote")]
colnames(links) <- c("source", "target", "value")

# draw sankey network
networkD3::sankeyNetwork(Links = links, Nodes = nodes, 
                         Source = 'source', 
                         Target = 'target', 
                         Value = 'value', 
                         NodeID = 'name',
                         units = 'votes') -> net

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
net
```

