---
title: "Exploratory Data Analysis"
author: "Nima Ramezani"
date: "07/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("~/Documents/software/R/projects/instacard/data/instacard_data.RData")
library(magrittr)
library(dplyr)
library(rml)
library(rutils)
library(highcharter)
library(tm)




source('~/Documents/software/R/projects/instacard/tools.R')

### Load NLP Clustering:
tx = readRDS('data/tm_object.rds')
tx$data$dataset$cluster_id = tx$data$CLS
products_pp = products %>% left_join(tx$data$dataset %>% 
                          rename(product_id = ID) %>% 
                          mutate(product_id = as.integer(as.character(product_id))) %>% 
                          select(product_id, cluster_id), by = c('product_id'))

### Split:
user_subset_train = orders$user_id %>% unique %>% sample(5000)
user_subset_test  = orders$user_id %>% unique %>% setdiff(user_subset_train) %>% sample(2000)

train_pack = build_training_pack(orders, products_pp, order_products_prior, customer_subset = user_subset_train)
test_pack  = build_training_pack(orders, products_pp, order_products_prior, customer_subset = user_subset_test)

### Build Features and Labels:
X_train = build_features(train_pack$feature_dataset)
X_test  = build_features(test_pack$feature_dataset)

y_train = X_train %>% select(user_id, product_id) %>% build_labels(train_pack$label_dataset)
y_test  = X_test %>% select(user_id, product_id) %>% build_labels(test_pack$label_dataset)
```

### Product Profile:
Let's have a closer look into our products:

# List of top 20 most popular products:
```{r most_popular_products}
pp1 = X_train %>% distinct(product_id, TotalProductOrdered) %>% 
  left_join(products_pp) %>% arrange(desc(TotalProductOrdered))

pp1 %>% arrange(desc(TotalProductOrdered)) %>% head(20) %>% knitr::kable()
```
Terms **Organic** appears a lot among the most popular products. 
It can also be observed that 
banana, strawberry, baby spinach, avocado and limes are among the most wanted products. 
These are mostly fruit and vegetable. 
It would be good to have a look at the keywords in the names of the most popular products.
Building a document-term matrix from the text of product titkes would be useful.
We can create a word-cload to see which terms are mostly used:

```{r product_wordcload}
texer::TEXT.MINER(pp1, text_col = 'product_name', id_col = 'product_id') -> tx
tx$settings$sparsity = 0.98

tx$plot.wordCloud()
```
It can be observed that words organic Chocolate, cheese and free are used more often in naming the products. However, this word cloud does not consider the popularity of the products.
So we created a weighted wordcloud which multiplies each word by the total number of orders of the product 
in which the term is used:
```{r product_popularity_wordcloud}
pp1 %>% 
  left_join(tx$data$dataset %>% 
    mutate(rn = sequence(nrow(.)),
           product_id = as.integer(as.character(ID))) %>% 
      select(product_id, rn), 
    by = 'product_id') -> pp2
  
dtm = tx$get.dtm() %>% as.matrix %>% {.[pp2$rn,]}
tdm = t(dtm)
wfq = t(pp2$TotalProductOrdered*tdm) %>% colSums(na.rm = T)
data.frame(word = names(wfq), freq = wfq) %>% arrange(desc(freq)) %>% head(500) %>% wordcloud2::wordcloud2()
```

## Unsupervised NLP clustering on product names:

We know that the likelihood of a customer buying a product can depend on 
wether of not a similar product was ordered in the customer's previous order or older orders before that. 
But how can we determine which products are **similar**?
Products are grouped in aisles which are expected to have similar products. 
It is good to consider count of products ordered within the aisle associated with the product in the previous customer orders.
However, there might be many non-similar products in a single aisle, so 
we need a more accurate grouping of features to ensure each group contain really similar products.
NLP clustering and topic modelling are two ways to adress this problem.

With NLP clustering we cluster products based on the similarity of their names. 
<!-- We use **binary** metric to quantify the similarity between products. -->
The more words two products' names have in common, the closer they are.
We use k-means to cluster the products with an elbow plot to determine the best number of clusters.




```{r customer_profile}
clusters = tx$clust(nc = 200)
```


```{r product_profile_2}
product_profile$TotalProductOrdered %>% hist
```
Distribution of **TotalProductOrdered** looks like exponential. However exponential is too simple and cannot explain the shape completely. Let's have a look at the tail of the distribution (least popular products):
```{r product_profile_2}
product_profile$TotalProductOrdered %>% {.[.<1000]} %>% hist(breaks = 1000)
```
Looking at the distribution of **TotalProductOrdered** in logarithmic scale, gives a better understanding of the distribution:
```{r product_profile_3}
product_profile$TotalProductOrdered %>% log(base = 10) %>% hist(breaks = 10000)
```


## Popularity vs Reorders

More popular products have been more reordered which is expected:

```{r product_profile_3}
product_profile %>% plotly::plot_ly(x = ~ProductReordersNormalized, y = ~ProductPopularity, type = 'scatter')
```

## Most popular products of each aisle:

```{r product_profile_4}
product_profile %>% 
  mutate(product_name = as.factor(product_name)) %>% 
  group_by(aisle_id) %>% 
  mutate(ProductPerAislePopularity = TotalProductOrdered/sum(TotalProductOrdered)) %>% 
  do({arrange(., desc(ProductPerAislePopularity)) %>% head(10)}) %>% 
  ungroup
```
