---
title: "Flexdashboard"
output:
  flexdashboard::flex_dashboard:
  vertical_layout: scroll
theme: cosmo
---

This is just minimal code to set up a Dashboard in R using [flexdashboard](http://rmarkdown.rstudio.com/flexdashboard/layouts.html).


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(readr)
library(highcharter)

train <- read_csv('train.csv')
train$Pclass <- as.factor(train$Pclass)
train$Embarked <- as.factor(train$Embarked)
```

Sample Layout 1 {data-orientation=rows data-icon="fa-bar-chart"}
=====================================

## Row 1 {data-height=110}

### Passengers of the Titanic

```{r}
valueBox(2222, icon = "fa-ship", color="rgb(100,100,100)")
```

### Percentage of survivors

```{r}
valueBox("31.6 %", icon = "fa-heart", color="rgb(200,100,100)")
```

### Water temperature

```{r}
valueBox("-2°C", icon = "fa-life-ring",color="rgb(26,110,204)")
```


## Row 2 {data-height=500}

### Age

```{r}
a <- density(train$Age[train$Sex == "female" & !is.na(train$Age)])
b <- density(train$Age[train$Sex == "male" & !is.na(train$Age)])
df <- data.frame(Age=c(a$x,b$x),Density=c(a$y,b$y),Sex=c(rep("female",length(a$x)),rep("male",length(b$x))))
hchart(df,type="area",hcaes(x=Age,y=Density,group=Sex),lineWidth=3, fillOpacity=0.2, color=c("#FFC0Cb","#44AAFF"),marker=list(radius=1))
```



## Row 3 {data-height=450}

### Port of Embarkation

```{r}
ggplot(train,aes(x=Embarked,y=Survived, fill=Embarked)) + geom_bar(stat="summary")
```

### Passenger Class

```{r}
ggplot(train,aes(x=Pclass,y=Survived, fill=Pclass)) + geom_bar(stat="summary")
```

Sample Layout 2 {data-icon="fa-area-chart"}
=====================================


Column {data-width=450}
-------------------------------------

### Kernel Finished

```{r}
rate <- 95
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Number of votes

```{r}
gauge(19, min = 0, max = 30, gaugeSectors(
  success = c(22, 30), warning = c(12, 21), danger = c(0, 11)
))
```

### Passenger Class

```{r}
ggplot(train,aes(x=Pclass,y=Survived, fill=Pclass)) + geom_bar(stat="summary")
```

Column {data-width=450}
-------------------------------------

### Port of Embarkation

```{r}
ggplot(train,aes(x=Embarked,y=Survived, fill=Embarked)) + geom_bar(stat="summary")
```

### Chart 3

```{r}
ggplot(train,aes(x=Age, color=Sex)) + geom_density()
```
